Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-11 manuscript/manuscript.tex
updated ms

We would like to thank the authors of the original studies we've analyzed,
including Neda Barghi, Christian Schl{\"o}tterer, John Kelly, Kimberly Hughes,
Frank Chan, Campbell Rolian, Nick Barton, Alan Bergland, and Dmitri Petrov. We
would also like to thank Doc Edge for helpful statistical advice, and Matt
Osmond, Erin Calfee, Andy Kern, Sivan Yair, \vb{Chuck Langley, Dave Begun, and
Michael Turelli} for helpful discussions. \vb{Additionally, we thank Guy Sella
and one additional anonymous reviewer for greatly improving the manuscript}.
This research was supported by an NSF Graduate Research Fellowship grant
awarded to VB (1650042), and NIH (R01-GM108779) and NSF (1353380) awarded to
GC.

>>>>

\vb{We would like to thank the authors of the original studies we have analyzed,
including Neda Barghi, Nick Barton, Alan Bergland, Frank Chan, Kimberly Hughes,
John Kelly, Dmitri Petrov, Campbell Rolian, Christian Schl{\"o}tterer. We would
also like to thank Doc Edge for helpful statistical advice, and Dave Begun,
Erin Calfee, Sarah Friedman, Andy Kern, Chuck Langley, and Michael Turelli,
Matt Osmond, Peter Ralph, Sivan Yair for helpful discussions. Additionally, we
thank Guy Sella and an anonymous reviewer whose comments greatly improved the
manuscript. This research was supported by an NSF Graduate Research Fellowship
grant awarded to VB (1650042), and NIH (R01-GM108779) and NSF (1353380) awarded
to GC.}
